\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}

A great deal of thanks are due to my supervisors, Ricardo Schiavon and Rob Crain, who have provided me with an immeasurable amount of support, alongside guidance and friendship, and who gave me the freedom to develop my own ideas whilst always providing sound scientific advice and critical intellectual input. I also thank my third supervisor, Ian McCarthy, for the provision of essential scientific scepticism. Among the many other faculty members at the ARI who have supported me, I would also like to heartily thank Marie Martig, who provided me with many important insights into my work. All my colleagues at the ARI, and in particular my friends Emma Beasor, Ashley Barnes and Lawrence Short, have been a pleasure to work with, and for that I thank them all whole-heartedly. 

In thanking my mentors, I would be remiss not to mention the encouragement and support which I have received from Jo Bovy and the Galactic Astrophysics group at the University of Toronto. Jo showed me the true art behind Bayesian statistics and re-introduced me to the beautiful field of Galactic dynamics. His mentorship has been invaluable throughout my studies. I was thankful for the hospitality of the Dunlap Institute and the Department of Astrophysics at the University of Toronto for multiple visits over the course of my PhD, without which this collaboration would not have been possible. 

Additionally, and in the spirit of important collaborations, I would like to give great thanks to the SDSS and all those involved with it (in APOGEE and beyond), and to the EAGLE team. Among these collaborators, individual thanks are due to Friedrich Anders, Borja Anguiano, Rachael Beaton, Richard Bower, Katia Cunha, Diane Feuillet, Misha Haywood, Keith Hawkins, Michael Hayden, Chris Hayes, Sten Hasselquist, Jon Holtzman, Jason Hunt, Jennifer Johnson, Steve Majewski, Paola Di Matteo, Andrea Miglio, Ivan Minchev, Elena d'Onghia, Marc Pinsonneault, Carlos Allende Prieto, Natalie Price-Jones, Joop Schaye, Matthew Shetrone, Victor Silva-Aguirre, Verne Smith, David Spergel, Tom Theuns, Yuan-Sen Ting, and Gail Zasowski who have all provided insightful ideas, comments, data, or supportive collaborations. I would also like to warmly thank Daisuke Kawata, Andreea Font, and David Carter, who examined this thesis and with whom I had an enlightening and helpful discussion during my defence of it. Their comments and suggestions both improved the thesis and provided good opportunity for further study.


I thank my Mum, who gave me the resilience to pull this off, and my Dad, who will always be the \emph{real} scientist. My sister, Alice, has always been there for me. All of them have always supported me in so many ways and I cant be thankful enough for that. My uncle, Mark, has been an academic mentor since I began at university, and was the ideal second on this climb. Also, thanks to my brilliant family-in-law, the `usual suspects' and to all my great friends from university, who have been there for me always. 

Finally, and to the highest order, thanks to my wonderful wife, Laura. I would follow you to the end of the earth, and I never doubt you would do the same for me. Your never ceasing consideration and support for me made this happen. Thank you.

\newpage

The funding for this PhD was provided by an STFC Studentship. The project made use of high performance computing facilities at Liverpool John Moores University, partly funded by the Royal Society and LJMU’s Faculty of Engineering and Technology. The Virgo Consortium are acknowledged for making their simulation data available. The EAGLE simulations were performed using the DiRAC-2 facility at Durham, managed by the ICC, and the PRACE facility Curie based in France at TGCC, CEA, Bruy\'eres-le-Chatel.

This work has made use of data from the European Space Agency (ESA)
mission Gaia (~\url{http://www.cosmos.esa.int/gaia}), processed by
the Gaia Data Processing and Analysis Consortium (DPAC,
~\url{http://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding
for the DPAC has been provided by national institutions, in particular
the institutions participating in the Gaia Multilateral Agreement.

Funding for the Sloan Digital Sky Survey III and IV was provided by the Alfred P. Sloan Foundation, the U.S. Department of Energy Office of Science, and the Participating Institutions. SDSS-III and SDSS-IV acknowledge
support and resources from the Center for High-Performance Computing at
the University of Utah. The SDSS web site is \url{www.sdss.org}.

All analyses and plots presented in this thesis used \texttt{iPython}, and packages in the \texttt{SciPy} ecosystem \citep{Jones:2001aa,4160265,4160251,5725236}.


\vfill
{\sc \AuthorName \hfill\today}